### 2020-10-07 report/draft.tex
fixed GA duration from value to range in Table 1

    Finally, $\delta$ is an extra mortality term defined as
    \[
      \begin{cases}
        d & \mbox{if } t < t_{AE} \\
        0 & \mbox{if } t > t_{AE}
      \end{cases}
    \]
    The parameters values and ranges are reported in \textbf{Table~\ref{tbl1}}.
    %
    \begin{table}
      \centering
      {%
        \begin{tabular}{@{}llccr@{}}
          \toprule
          \textbf{Variable}&\textbf{Meaning} & \textbf{Units} & \textbf{Value} & \textbf{Reference}\\
          \midrule
          ${P}_{0}$       & initial concentration of $P$ cells         & cells/ml          & 4E3         & Experiment detailed in the paper\\
          $\alpha$        & fraction of $P$ that will generate $F_{1}$ & ---               & [0.01, 0.2] & Explored via simulations\\
          $r_{P}$         & net growth rate of $P$                     & $\text{day}^{-1}$ & [1, 3]      & Explored via simulations\\ 
          $r_{F_{1}}$     & net growth rate of $F_{1}$                 & $\text{day}^{-1}$ & 1           & ---\\
          $t_{AE}$        & end day of the growth arrest               & day               & 4           & Experiment detailed in the paper\\
          $t_{F_{1}I}$    & day of appearence of the offspring         & day               & 3           & Experiment detailed in the paper\\
          $L_{0,P}$       & starting length for $P$ cells              & $\mu$m            & 40          & Experiment detailed in the paper\\
          $L_{0,{F_{1}}}$ & starting length for $F_{1}$ cells          & $\mu$m            & 80          & Experiment detailed in the paper\\
          $d$             & gametogenesis-induced extra mortality      & day               & [0.1, 0.9]  & Explored via simulations\\
          \bottomrule
        \end{tabular}
       }
      \caption{Values and ranges for model parameters}\label{tbl1}
    \end{table}
%
  \section*{Results}
    \textbf{Fig.~\ref{fdyn}} shows the relative variation of allometric growth (panel a), the size reduction of $P$ and $F_{1}$ during the simulations (panel b) and variation of $P$ and $F_{1}$ densities for two different sets' of parameter values (panels c and d) \textbf{reported in the legend}.
    We simulated a wide set of scenarios corresponding to the chosen ranges of variation of the different parameters reported in \textbf{Table~\ref{tbl1}} focusing, as output variable, on the recruitment success of the offsprings quantified as the ratio between $F_{1}$ and $P$, after ten days from the start of mating.
    \textbf{Fig.~\ref{swep}} shows the logarithm of the ratio in relation to different values of the parameters or their combination.
    %
    \begin{figure}[p]
      \includegraphics[width=\linewidth]{imgs/Figpan.pdf}
      \caption{\textbf{Simulated size dependent growth and impact on the population dynamics} ---
      \textit{(a)} dependence of specific growth rate on cell length;
      \textit{(b)} Size reduction for the two sub-populations;
      examples of simulation outputs whith $r_{p} = 1.82$ \textit{(c)} and $r_{p} = 1$ \textit{(d)}.
      In \textit{(c)} and \textit{(d)}: $\alpha=0.012, d = 0.8$, all the other parameters as per \textbf{Tab.~\ref{tbl1}}.}\label{fdyn}
    \end{figure}
    %
    \begin{figure}[p]
      \centering
      \begin{subfigure}{\textwidth}
        \includegraphics[width=\linewidth]{imgs/a.pdf}
      \end{subfigure}

>>>>

    Finally, $\delta$ is an extra mortality term defined as
    \[
      \begin{cases}
        d & \mbox{if } t < t_{AE} \\
        0 & \mbox{if } t > t_{AE}
      \end{cases}
    \]
    The parameters values and ranges are reported in \textbf{Table~\ref{tbl1}}.
    %
    \begin{table}
      \centering
      {%
        \begin{tabular}{@{}llccr@{}}
          \toprule
          \textbf{Variable}&\textbf{Meaning} & \textbf{Units} & \textbf{Value} & \textbf{Reference}\\
          \midrule
          ${P}_{0}$       & initial concentration of $P$ cells         & cells/ml          & 4E3         & Experiment detailed in the paper\\
          $\alpha$        & fraction of $P$ that will generate $F_{1}$ & ---               & [0.01, 0.2] & Explored via simulations\\
          $r_{P}$         & net growth rate of $P$                     & $\text{day}^{-1}$ & [1, 3]      & Explored via simulations\\ 
          $r_{F_{1}}$     & net growth rate of $F_{1}$                 & $\text{day}^{-1}$ & 1           & ---\\
          $t_{AE}$        & end day of the growth arrest               & day               & [2,6]       & Explored via simulations\\
          $t_{F_{1}I}$    & day of appearence of the offspring         & day               & 3           & Experiment detailed in the paper\\
          $L_{0,P}$       & starting length for $P$ cells              & $\mu$m            & 40          & Experiment detailed in the paper\\
          $L_{0,{F_{1}}}$ & starting length for $F_{1}$ cells          & $\mu$m            & 80          & Experiment detailed in the paper\\
          $d$             & gametogenesis-induced extra mortality      & day               & [0.1, 0.9]  & Explored via simulations\\
          \bottomrule
        \end{tabular}
       }
      \caption{Values and ranges for model parameters}\label{tbl1}
    \end{table}
%
  \section*{Results}
    \textbf{Fig.~\ref{fdyn}} shows the relative variation of allometric growth (panel a), the size reduction of $P$ and $F_{1}$ during the simulations (panel b) and variation of $P$ and $F_{1}$ densities for two different sets' of parameter values (panels c and d) \textbf{reported in the legend}.
    We simulated a wide set of scenarios corresponding to the chosen ranges of variation of the different parameters reported in \textbf{Table~\ref{tbl1}} focusing, as output variable, on the recruitment success of the offsprings quantified as the ratio between $F_{1}$ and $P$, after ten days from the start of mating.
    \textbf{Fig.~\ref{swep}} shows the logarithm of the ratio in relation to different values of the parameters or their combination.
    %
    \begin{figure}[p]
      \includegraphics[width=\linewidth]{imgs/Figpan.pdf}
      \caption{\textbf{Simulated size dependent growth and impact on the population dynamics} ---
      \textit{(a)} dependence of specific growth rate on cell length;
      \textit{(b)} Size reduction for the two sub-populations;
      examples of simulation outputs whith $r_{p} = 1.82$ \textit{(c)} and $r_{p} = 1$ \textit{(d)}.
      In \textit{(c)} and \textit{(d)}: $\alpha=0.012, d = 0.8$, all the other parameters as per \textbf{Tab.~\ref{tbl1}}.}\label{fdyn}
    \end{figure}
    %
    \begin{figure}[p]
      \centering
      \begin{subfigure}{\textwidth}
        \includegraphics[width=\linewidth]{imgs/a.pdf}
      \end{subfigure}
